### 2016-03-21 manuscript.Rnw
fix typos
include Scott's comments on pre-print

The R programming language is a popular tool for phylogenetics and comparative
analysis. The R packages \texttt{ape} \citep{Paradis2004}, \texttt{phylobase}
\citep{phylobase-0.8.0}, and \texttt{RNeXML} \citep{Boettiger2015} each provide
functions to import and manipulate trees within R and save the results in
standard data formats. Additional packages including \texttt{phytools}
\citep{Revell2012}, \texttt{geiger} \citep{Pennell2014-geiger}, and
\texttt{ggtree} \citep{Yu-ggtree}, allow users to analyze and visualize data in
a phylogenetic context (see
\url{https://cran.r-project.org/web/views/Phylogenetics.html} for a
comprehensive list of phylogenetics packages in R). In addition to packages for
phylogenetic and comparative analyses, a growing number of R packages allows
users to query and access data from the web (e.g. \texttt{rFISHBASE}
\citep{Boettiger2012}, \texttt{rAvis} \citep{Varela2014}, and \texttt{paleoDB}
\citep{Varela2015}), such that data associated with taxa in a given phylogeny
can be obtained directly in R.

@@

Here we present \texttt{rotl}, and R package that allows users to download
phylogenetic and taxonomic data from the OTL directly in R. \texttt{rotl} takes
advantage of OTL's Application Programming Interfaces (APIs) to access sub-trees
from the synthetic Open Tree, as well as the published source trees that
contribute to the synthesis. By providing direct access to high quality
phylogenetic data in R, \texttt{rotl} fills a key gap in typical comparative
analysis workflows, and extends the degree to which R supports reproducible
research in phylogenetics and comparative biology.

@@

Before a researcher can use the Open Tree to retrieve relationships among a set
of taxa, they first need to match the taxon names in their dataset with records
in the Open Tree Taxonomy (OTT). The TNRS allows users to search for taxon
names, and retreive identifiers for each matching taxon. We demonstrate the use
of the TNRS within \texttt{rotl} by searching for taxonomic records associated
with several model organisms.

>>>>

The R programming language is a popular tool for phylogenetics and comparative
analysis. The R packages \texttt{ape} \citep{Paradis2004}, \texttt{phylobase}
\citep{phylobase-0.8.0}, and \texttt{RNeXML} \citep{Boettiger2015} each provide
functions to import and manipulate trees within R and save the results in
standard data formats. Additional packages including \texttt{phytools}
\citep{Revell2012}, \texttt{geiger} \citep{Pennell2014-geiger}, and
\texttt{ggtree} \citep{Yu-ggtree}, allow users to analyze and visualize data in
a phylogenetic context (see
\url{https://cran.r-project.org/web/views/Phylogenetics.html} for a
comprehensive list of phylogenetics packages in R). In addition to packages for
phylogenetic and comparative analyses, a growing number of R packages allows
users to query and access data from the web (e.g. \texttt{rFISHBASE}
\citep{Boettiger2012}, \texttt{rAvis} \citep{Varela2014}, and \texttt{paleobioDB}
\citep{Varela2015}), such that data associated with taxa in a given phylogeny
can be obtained directly in R.

@@

Here we present \texttt{rotl}, an R package that allows users to download
phylogenetic and taxonomic data from the OTL directly in R. \texttt{rotl} takes
advantage of OTL's Application Programming Interfaces (APIs) to access sub-trees
from the synthetic Open Tree, as well as the published source trees that
contribute to the synthesis. By providing direct access to high quality
phylogenetic data in R, \texttt{rotl} fills a key gap in typical comparative
analysis workflows, and extends the degree to which R supports reproducible
research in phylogenetics and comparative biology.

@@

Before a researcher can use the Open Tree to retrieve relationships among a set
of taxa, they first need to match the taxon names in their dataset with records
in the Open Tree Taxonomy (OTT). OTL's taxonomic names resolution service (TNRS)
combines information from multiple services (e.g., National Center for
Biotechnology Information [NCBI], World Register for Marine Species [WoRMS],
Global Biodiversity Information Facility [GBIF]) and allows users to search for
taxon names, and retreive identifiers for each matching taxon. We demonstrate
the use of the TNRS within \texttt{rotl} by searching for taxonomic records
associated with several model organisms.
